raster_brick_stuff

### 2018-09-28 src/raster_brick_stuff.Rmd
probably not useful stuff for my netcdf data extraction...

# Package dependencies
You can load them using the following code which uses a function called [ipak](https://gist.github.com/stevenworthington/3178163). 
Note this function checks to see if the packages are installed first.
```{r pre-install packages, suppressMessages(expr)}
packages <- c("rgdal", "raster", "ncdf4", "RNetCDF", "sp", "parallel", "magrittr", "data.table") 
source("../src/ipak.R")
ipak(packages)
```

For the parallel computing, detect cores automatically (leave one free though).
```{r}
cores <- detectCores() - 1
```

@@

```{r}
library("ncdf4")
source("../src/netcdf_to_rasterbrick.R")

```

>>>>

# Package dependencies
You can install and load them using the following code which uses a function called [ipak](https://gist.github.com/stevenworthington/3178163). 
Note this function checks to see if the packages are installed first. If they are not installed, it will do so before loading
```{r pre-install packages, suppressMessages(expr)}
packages <- c("rgdal", "raster", "ncdf4", "RNetCDF", "sp", "parallel", "magrittr", "data.table") 
source("../src/ipak.R")
ipak(packages)
```

For the parallel computing (this will make things faster), detect cores automatically (leave one free though).
```{r}
cores <- detectCores() - 1
```

@@

Tell R where to find your data and where to spit out the output
```{r data_paths}
envdata_path <- "../data/env/netcdf"
projected_path <- "../data/env"
output_path <- "../output/env"
```
